UQWorld: an Applied UQ Community

### 2019-05-07 latex/BeamerGPR.tex
Minor edit

We tried to get some ideas for our UQ community based on
our understanding of the \emph{natural} audience, i.e., \textbf{UQLab users}:

@@

How can we know more of our audience up to the present?

@@

\begin{itemize}
  \item Dakota maintains mailing lists,
        but this is 2019\footnote{not that mailing list has become obsolete, but it definitely has its downsides for a community}.
  \item OpenTurns maintains a blog, but not maintained.
  \item Otherwise, zero relevant results from Google search
        for ``uncertainty quantification community'' or ``uncertainty quantification forum''.
\end{itemize}

@@

\begin{itemize}
  \item UQ practitioners and researchers and
  \item UQLab users
\end{itemize}

>>>>

We tried to get some ideas for our UQ community based on
our understanding of the \emph{apparent} audience, i.e., \textbf{UQLab users}:

@@

How can we know more of our audience, up to the present?

@@

\begin{itemize}
  \item Dakota maintains mailing lists,
        but this is 2019\footnote{not that mailing list has become obsolete, but it definitely has its downsides for a community}.
  \item OpenTurns (barely) maintains a blog (last post july 2019, peak posts in 2011, no public discussions) 
  \item Otherwise, zero relevant results from Google search
        for ``uncertainty quantification community'' or ``uncertainty quantification forum''.
\end{itemize}

@@

\begin{itemize}
  \item UQ practitioners and researchers, and
  \item UQLab users
\end{itemize}
